---
title: "Lab 10"
author: "Shraddha Tamang"
date: "4/1/2020"
output: html_document
---

### The data used for graphs below are taken from Jonh Hopkins Github site
```{r, warnings=FALSE, message=FALSE, echo=FALSE }
library(tidyverse)
library(maps)
library(mapdata)
library(lubridate)
library(viridis)
library(wesanderson)
```

### Exercise

```{r, warning=FALSE, message=FALSE, echo=FALSE}
daily_report <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-31-2020.csv")) %>% 
  rename(Long = "Long_") 
    
ggplot(daily_report, aes(x = Long, y = Lat, size = Deaths/1000)) +
    borders("world", colour = NA, fill = "grey90") +
    theme_bw() +
    geom_point(shape = 21, color='blue', fill='blue', alpha = 0.5) +
    labs(title = 'World COVID-19 Death cases',x = '', y = '',
        size="Cases (x1000))") +
    theme(legend.position = "right") +
    coord_fixed(ratio=1.5)
```


### The above picture shows the death cases of COVID-19 around the world on April 31,2020.

```{r,warning=FALSE, message=FALSE, echo=FALSE}
daily_report <-   read_csv(url("https://raw.githubusercontent.com/shraddhatama/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-23-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Country_Region == "US") %>% 
  filter (!Province_State %in% c("Alaska","Hawaii", "American Samoa",
                  "Puerto Rico","Northern Mariana Islands", 
                  "Virgin Islands", "Recovered", "Guam", "Grand Princess",
                  "District of Columbia", "Diamond Princess")) %>% 
  filter(Lat > 0)

ggplot(daily_report, aes(x = Long, y = Lat, size = Deaths/1000)) +
    borders("state", colour = "blue", fill = "grey90") +
    theme_bw() +
    geom_point(shape = 21, color='orange', fill='orange', alpha = 0.5) +
    labs(title = 'COVID-19 Death Cases in the US', x = '', y = '',
        size="Cases (x1000))") +
    theme(legend.position = "right") +
    coord_fixed(ratio=1.5)
```


### The above graph shows the death cases of COVID-19 in the US on April 23, 2020. This graph excludes Alaska,Hawaii, American Samoa, Puerto Rico, Northern Mariana Islands, Virgin Islands, Guam,Grand Princess, District of Columbia, Diamond Princess. 

```{r, warning=FALSE, message=FALSE, echo=FALSE}
daily_report <- read_csv(url("https://raw.githubusercontent.com/shraddhatama/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-24-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(Deaths = sum(Deaths)) %>% 
  mutate(Province_State = tolower(Province_State))

# load the US map data
us <- map_data("state")
# We need to join the us map data with our daily report to make one data frame/tibble
state_join <- left_join(us, daily_report, by = c("region" = "Province_State"))

# plot state map
ggplot(data = us, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
# Add data layer
  geom_polygon(data = state_join, aes(fill = Deaths), color = "white") +
  geom_polygon(color = "black", fill = NA) +
  scale_fill_gradient(trans = "log10") +
  labs(title = "COVID-19 Deaths Cases in the US'")
```


### The above picture shows the death cases of COVID-19 in the US on April 24,2020.

```{r, warning=FALSE, message=FALSE, echo=FALSE}
# plot state map
ggplot(data = us, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
# Add data layer
  geom_polygon(data = state_join, aes(fill = Deaths), color = "white") +
  geom_polygon(color = "black", fill = NA) +
  scale_fill_gradientn(colours = 
                         wes_palette("Royal1", 100, type = "continuous"),
                         trans = "log10") +
  labs(title = "COVID-19 Death Cases in the US'")
```


### The above picture shows the death cases of COVID-19 in the US on April 24,2020.

```{r, warning=FALSE, message=FALSE, echo=FALSE}
daily_report <-read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-28-2020.csv")) %>% 
  rename(Long = "Long_") %>%
  filter(Province_State == "New York") %>%
  group_by(Admin2) %>% 
  summarize(Deaths = sum(Deaths)) %>%
  mutate(Admin2 = tolower(Admin2))

us <- map_data("state")
nyc_us <- subset(us, region == "new york")
counties <- map_data("county")
nyc_county <- subset(counties, region == "new york")

state_join <- left_join(nyc_county, daily_report, by = c("subregion" = "Admin2")) 

# plot state map
ggplot(data = nyc_county, mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) + 
# Add data layer
  geom_polygon(data = state_join, aes(fill = Deaths), color = "white") +
  scale_fill_gradientn(colours =
                  wes_palette("Rushmore1", 100, type = "continuous"),
trans = "log10") +
  labs(title = "COVID-19 Deaths in New York'")
```


### The above picture shows the death cases of corona virus at New York on April 28, 2020.
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(plotly)

ggplotly(
  ggplot(data = nyc_county, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
# Add data layer
  geom_polygon(data = state_join, aes(fill = Deaths), color = "black") +
    scale_fill_gradientn(colours = 
                         wes_palette("Royal1", 100, type = "continuous")) +
  ggtitle("COVID-19 Death Cases in NY") +
# Cleaning up the graph
  labs(x=NULL, y=NULL) +
  theme(panel.border = element_blank()) +
  theme(panel.background = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(axis.text = element_blank())
)
```


### The above picture shows an interactive graph, the death cases of corona virus at New York on April 28, 2020.

```{r, warning=FALSE, message=FALSE, echo=FALSE}
time_series_confirmed_long <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")) %>%
  rename(Province_State = "Province/State", Country_Region = "Country/Region")  %>% 
               pivot_longer(-c(Province_State, Country_Region, Lat, Long),
                            names_to = "Date", values_to = "Confirmed") 

# Let's get the times series data for deaths

time_series_deaths_long <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")) %>%
  rename(Province_State = "Province/State", Country_Region = "Country/Region")  %>% 
  pivot_longer(-c(Province_State, Country_Region, Lat, Long),
               names_to = "Date", values_to = "Deaths")

time_series_recovered_long <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv")) %>%
  rename(Province_State = "Province/State", Country_Region = "Country/Region") %>% 
  pivot_longer(-c(Province_State, Country_Region, Lat, Long),
               names_to = "Date", values_to = "Recovered")

# Create Keys 

time_series_confirmed_long <- time_series_confirmed_long %>% 
  unite(Key, Province_State, Country_Region, Date, sep = ".", remove = FALSE)

time_series_deaths_long <- time_series_deaths_long %>% 
  unite(Key, Province_State, Country_Region, Date, sep = ".") %>% 
  select(Key, Deaths)

time_series_recovered_long <- time_series_recovered_long %>% 
  unite(Key, Province_State, Country_Region, Date, sep = ".") %>% 
  select(Key, Recovered)

# Join tables
time_series_long_joined <- full_join(time_series_confirmed_long,
              time_series_deaths_long, by = c("Key"))

time_series_long_joined <- full_join(time_series_long_joined,
              time_series_recovered_long, by = c("Key")) %>% 
    select(-Key)

# Reformat the data
time_series_long_joined$Date <- mdy(time_series_long_joined$Date)

# Create Report table with counts
time_series_long_joined_counts <- time_series_long_joined %>% 
  pivot_longer(-c(Province_State, Country_Region, Lat, Long, Date),
               names_to = "Report_Type", values_to = "Counts")
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
library(ggplot2)
library(gganimate)
library(transformr)
theme_set(theme_bw())
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
data_time <- time_series_long_joined %>% 
    group_by(Country_Region,Date) %>% 
    summarise_at(c("Confirmed", "Deaths", "Recovered"), sum) %>% 
    filter (Country_Region %in% c("Australia","India", "France","Mexico","Italy")) 

p <- ggplot(data_time, aes(x = Date,  y = Deaths, color = Country_Region)) + 
      geom_point() +
      geom_line() +
      ggtitle("Deaths COVID-19 Cases") +
      geom_point(aes(group = seq_along(Date))) +
      transition_reveal(Date) 
    
animate(p, end_pause = 15)
```



### The above picture shows an animation of death cases in Australia, India, France, Mexico, and Italy. 
```{r, warning=FALSE, message=FALSE, echo=FALSE}
covid <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")) %>%
  rename(Province_State= "Province/State", Country_Region = "Country/Region") %>%
  pivot_longer(-c(Province_State, Country_Region, Lat, Long),
               names_to = "Date", values_to = "Deaths") %>%
  mutate(Date = mdy(Date) - days(1),
         Place = paste(Lat,Long,sep="_")) %>%
# Summarizes state and province information
  group_by(Place,Date) %>%
  summarise(cumulative_cases = ifelse(sum(Deaths)>0,
                                  sum(Deaths),NA_real_),
            Lat = mean(Lat),
            Long = mean(Long)) %>%
  mutate(Pandemic_day = as.numeric(Date - min(Date)))

world <- ggplot(covid,aes(x = Long, y = Lat, size = cumulative_cases/1000)) +
  borders("world", colour = "gray50", fill = "grey90") +
  theme_bw() +
  geom_point(color='blue', alpha = .5) +
  labs(title = 'Pandemic Day: {frame}',x = '', y = '',
       size="Cases (x1000))") +
  theme(legend.position = "right") +
  coord_fixed(ratio=1.3)+
  transition_time(Date) +
  enter_fade()

animate(world, renderer = gifski_renderer(), end_pause = 30)

```


### The above picture shows an animation of death cases as the pandemic days goes up.
